\documentclass[12pt, letterpaper]{article}

\usepackage{geometry}    % For page layout
\geometry{margin=1 in}
\usepackage{hyperref}
\hypersetup{
    colorlinks=false,
    linkcolor=blue,
    urlcolor=blue,
    pdfborder={0 0 0}
}

\title{Research in AI, ML \& SWE}
\author{}
\date{}

\begin{document}
\maketitle

\setcounter{tocdepth}{2}
\tableofcontents
\newpage

\section{Prominent Authors}

\subsection{Foundational AI and Deep Learning Pioneers}
\begin{itemize}
    \item \textbf{Geoffrey Hinton} – University of Toronto and Google DeepMind
    \item \textbf{Yoshua Bengio} – University of Montreal
    \item \textbf{Yann LeCun} – Meta (Facebook AI Research) and New York University
\end{itemize}

\subsection{Reinforcement Learning and Decision Intelligence}
\begin{itemize}
    \item \textbf{Richard Sutton} – University of Alberta and DeepMind
    \item \textbf{David Silver} – DeepMind
    \item \textbf{Pieter Abbeel} – University of California, Berkeley
\end{itemize}

\subsection{Probabilistic Models, Causality, and Statistical ML}
\begin{itemize}
    \item \textbf{Judea Pearl} – University of California, Los Angeles
    \item \textbf{Zoubin Ghahramani} – University of Cambridge and Google DeepMind
    \item \textbf{Michael Jordan} – University of California, Berkeley
\end{itemize}

\subsection{Computer Vision and Generative Models}
\begin{itemize}
    \item \textbf{Ian Goodfellow} – Apple (formerly Google Brain)
    \item \textbf{Fei-Fei Li} – Stanford University
    \item \textbf{Sergey Levine} – University of California, Berkeley
\end{itemize}

\subsection{Natural Language Processing (NLP)}
\begin{itemize}
    \item \textbf{Christopher Manning} – Stanford University
    \item \textbf{Jacob Devlin} – Google Research
    \item \textbf{Tomas Mikolov} – Czech Academy of Sciences (formerly Google)
\end{itemize}

\subsection{Transformers and Large Language Models}
\begin{itemize}
    \item \textbf{Ashish Vaswani} – Co-author of “Attention Is All You Need”
    \item \textbf{Noam Shazeer} – Co-founder of Character.AI (formerly Google)
    \item \textbf{Oriol Vinyals} – DeepMind
\end{itemize}

\subsection{AI Ethics, Fairness, and Societal Impact}
\begin{itemize}
    \item \textbf{Timnit Gebru} – Distributed AI Research Institute (DAIR)
    \item \textbf{Joy Buolamwini} – MIT Media Lab
\end{itemize}

\subsection{Foundational Contributors}
\begin{itemize}
    \item \textbf{Barry Boehm} – Known for the Spiral Model and Constructive Cost Model (COCOMO).
    \item \textbf{David L. Parnas} – Introduced information hiding and modular design principles.
    \item \textbf{Watts S. Humphrey} – Pioneer of software process improvement and the Capability Maturity Model (CMM).
    \item \textbf{Fred Brooks} – Author of “The Mythical Man-Month”; led IBM System/360 and OS/360 projects.
\end{itemize}

\subsection{Software Architecture and Design}
\begin{itemize}
    \item \textbf{Mary Shaw} – Early advocate of software architecture as a discipline.
    \item \textbf{David Garlan} – Co-developer of software architecture frameworks and architectural styles.
    \item \textbf{Grady Booch} – Co-creator of UML and Object-Oriented Design methods.
    \item \textbf{Ivar Jacobson} – Contributed to UML and use case–driven software engineering.
\end{itemize}

\subsection{Software Testing and Quality Assurance}
\begin{itemize}
    \item \textbf{Glenford Myers} – Author of “The Art of Software Testing.”
    \item \textbf{Cem Kaner} – Leading figure in practical software testing and test case design.
    \item \textbf{Mauro Pezzè} – Research on software testing, validation, and self-healing systems.
    \item \textbf{Michal Young} – Work on software testing and analysis tools.
\end{itemize}

\subsection{Empirical and Data-Driven Software Engineering}
\begin{itemize}
    \item \textbf{Victor Basili} – Introduced the Goal-Question-Metric (GQM) paradigm and empirical software engineering.
    \item \textbf{Forrest Shull} – Research on evidence-based software engineering practices.
    \item \textbf{Diomidis Spinellis} – Research on software analytics and large-scale software measurement.
    \item \textbf{Thomas Zimmermann} – Work on mining software repositories and empirical defect prediction.
\end{itemize}

\subsection{Requirements Engineering}
\begin{itemize}
    \item \textbf{Axel van Lamsweerde} – Known for goal-oriented requirements engineering.
    \item \textbf{Bashar Nuseibeh} – Research on requirements analysis and software evolution.
    \item \textbf{Alessandra Russo} – Contributions to formal methods in requirements and specification.
\end{itemize}

\subsection{Software Maintenance, Evolution, and Analytics}
\begin{itemize}
    \item \textbf{Audris Mockus} – Work on mining software repositories and software evolution.
    \item \textbf{Prem Devanbu} – Research in empirical software engineering and naturalness of code.
    \item \textbf{Michael W. Godfrey} – Contributions to software evolution and architecture recovery.
\end{itemize}

\subsection{Modern Software Engineering and AI in SE}
\begin{itemize}
    \item \textbf{Tim Menzies} – Research on AI-driven software analytics and defect prediction.
    \item \textbf{Thomas Zimmermann} – Applied machine learning to software quality prediction.
    \item \textbf{Andrian Marcus} – Research on software visualization and program comprehension.
\end{itemize}

\section{Prominent Conferences and Journals}

\subsection{Top-Tier AI / ML Conferences}

\begin{itemize}
    \item \textbf{NeurIPS} — Conference on Neural Information Processing Systems  
    \textit{Focus:} Core ML, deep learning, theory + practice.
    \item \textbf{ICML} — International Conference on Machine Learning  
    \textit{Focus:} Foundational ML research.
    \item \textbf{ICLR} — International Conference on Learning Representations  
    \textit{Focus:} Deep learning, representation learning.
    \item \textbf{AAAI} — Association for the Advancement of Artificial Intelligence  
    \textit{Focus:} Broad AI topics.
    \item \textbf{IJCAI} — International Joint Conference on Artificial Intelligence  
    \textit{Focus:} Classical + modern AI.
\end{itemize}

\subsection{Applied AI / Data Science Conferences}

\begin{itemize}
    \item \textbf{IEEE ICDM} — International Conference on Data Mining  
    \textit{Focus:} Applied data mining, pattern discovery.
    \item \textbf{ACM KDD} — Knowledge Discovery and Data Mining  
    \textit{Focus:} Data science, applied ML.
    \item \textbf{Springer / IEEE BigData, AIoT, SmartData}  
    \textit{Focus:} Applied AI in software, IoT, big data systems.
    \item \textbf{ACM / IEEE CIKM} — Conference on Information and Knowledge Management  
    \textit{Focus:} AI for information systems, data integration.
\end{itemize}

\subsection{Software Engineering + AI Conferences}

\begin{itemize}
    \item \textbf{IEEE / ACM ICSE} — International Conference on Software Engineering  
    \textit{Focus:} Top software engineering conference.
    \item \textbf{IEEE MSR} — Mining Software Repositories  
    \textit{Focus:} Using ML on codebases, bug reports, Git data.
    \item \textbf{IEEE ASE} — Automated Software Engineering  
    \textit{Focus:} ML-driven software automation.
    \item \textbf{ACM ESEC/FSE} — Empirical Software Engineering and Automation  
    \textit{Focus:} Empirical SE, automation, ML in development.
    \item \textbf{Springer EMSE} — Empirical Software Engineering (Journal)  
    \textit{Focus:} Journal for mature research in empirical SE.
\end{itemize}

\subsection{Trustworthy / Responsible AI Conferences}

\begin{itemize}
    \item \textbf{ACM FAccT} — Fairness, Accountability, and Transparency  
    \textit{Focus:} Ethics and governance in AI.
    \item \textbf{IEEE AIES} — AI, Ethics, and Society  
    \textit{Focus:} Responsible AI, AI safety.
    \item \textbf{Springer AI \& Society (Journal)}  
    \textit{Focus:} Interdisciplinary responsible AI research.
\end{itemize}

\subsection{Recommended Journals}

\begin{itemize}
    \item \textbf{IEEE Transactions on Neural Networks and Learning Systems (TNNLS)}  
    \textit{Focus:} Core ML \& neural networks.
    \item \textbf{IEEE Transactions on Software Engineering (TSE)}  
    \textit{Focus:} AI in SE, automation, quality, analysis.
    \item \textbf{ACM Transactions on Intelligent Systems and Technology (TIST)}  
    \textit{Focus:} Applied AI, intelligent systems.
    \item \textbf{Journal of Machine Learning Research (JMLR)}  
    \textit{Focus:} Foundational ML.
    \item \textbf{Springer Data Mining and Knowledge Discovery}  
    \textit{Focus:} Applied ML, data science.
    \item \textbf{Elsevier Information Sciences}  
    \textit{Focus:} Hybrid AI + system-based data analysis.
    \item \textbf{Wiley Software: Practice and Experience}  
    \textit{Focus:} Software systems, empirical AI-driven solutions.
\end{itemize}

\subsection{Practical Resources}

\begin{enumerate}
    \item \underline{\href{https://arxiv.org}{ArXiv}}
    \item \underline{\href{https://paperswithcode.com}{Papers with code}}
    \item \underline{\href{https://dl.acm.org/}{ACM Digital Library}}
    \item \underline{\href{https://ieeexplore.ieee.org/Xplore/home.jsp}{IEEE Xplore}}
    \item \underline{\href{https://www.springeropen.com/}{SpringerOpen}}
    \item \underline{\href{https://dspace.mit.edu/}{DSpaceMIT}}
    \item \underline{\href{https://www.semanticscholar.org/}{Semantic Scholar}}
    \item \underline{\href{https://scholar.google.com/}{Google Scholar}}
\end{enumerate}

These databases let you:
\begin{itemize}
    \item Search for conferences and journals in your field.
    \item Check paper formats and acceptance rates.
    \item Identify trending research topics.
\end{itemize}



\end{document}
